---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/"
)
library(dvesimpler)
```

## Overview

### Projct Notes

The development guides are available under `notes/`, see:

* [**Project Usage Notes**](notes/usage/README.md)


### Acknoledgements

> We greatly acknowledge the [University of Milano-Bicocca](http://www.unimib.it) "Data Science Lab" ([datalab](http://datalab.unimib.it)) 
> for supporting this work by providing computational resources.




### Features

The `dvesimpler` package is a simple R project template:

* supporting R package builder `as-cran`,
* packagin runtime environment (rstudio, dependencies) as a container image
* packagin project contents (code, scripts) as an executable container image
* externalize data directories symlinked relative to project root, 
* demo scripts, functions and tests.

### Runtime Environments

This project supports two different execution environments:

* `direct`: traditional execution environment that runs system installed R/RStudio (desktop).
* `containerized`: execution environment that runs a container image with a fully customizable R/RStudio (server) setup.


The `direct` model is simpler but with many limitations:
- it is "bound" to a single host and is based to a predefined R setup
- the system installed environment is periodically upgraded by management scripts, not customizable.
- these is no support for dependency versioning and remote execution.

The `containerized` model more complex, but presents many advantages:
- full control in runtime definition (R version, predefined packages)
- container images based on: [Rocker Project Images](https://www.rocker-project.org/images/)
- [renv](https://rstudio.github.io/renv/articles/renv.html) support for [Reproducible research](https://en.wikipedia.org/wiki/Reproducibility#Reproducible_research) project specification
- [Podman](https://podman.io/) containers enable remote execution and distribution, prerequisite for shared computaional resource access.
 
 

## Development Environment

### Project Dwevelopment Guides

* Build environment and execution scripts are documented in `./notes/usage`.

### Readme document update

This README.md is generated from README.Rmd. Please edit that file. To rebuild:

```{sh, eval = FALSE}

# in project base directory

./build.sh readme

```

This command can be run in container, by entering a shell in the inner environment

```{sh, eval = FALSE}

# externally, in project base directory

./runtime.sh sh

# internally, in project base directory

./build.sh readme

```



  
## Document Sample

### Code Evaluation

```{r, eval = TRUE}

salutation <- c( 
  dummy_hello(),
  dummy_hello("Earth"),
  dummy_hello("Moon", "'Night")
)

cat(salutation)

```



## Script Execution

### in Rsession

```{r, eval = TRUE}

# in project base directory

source("exec/dummy_runner.R")

```

### from command-line (inside container)

```{sh, eval = FALSE}

# in project base directory

./starter.sh


```

### from command-line (outside container)

```{sh, eval = FALSE}

# in project base directory

./worker.sh pack,exec


```


## Sample Usage

## GitLab Installation


```{r, eval = FALSE}

# install from gitlab
# install.packages("devtools")
devtools::install_gitlab("ub-dems-public/ds-labs/dve-sample-r")

```

### Basic demo
  
* `dummy_hello()` get default salutation


