---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/"
)
library(dvesimpler)
```

## Overview

The `dvesimpler` package is a simple R project template:

* supporting R package builder `as-cran`,
* packagine runtime environment (rstudio, dependencies) as a container image
* packagine project contents (code, scripts) as an executable container image
* externalize data directories symlinked relative to project root, 
* demo scripts, functions and tests.

## Development Environment

### Project Dwevelopment Guides

* Build environment and execution scripts are documented in `./notes/usage`.

### Readme document update

This README.md is generated from README.Rmd. Please edit that file. To rebuild:

```{sh, eval = FALSE}

# in project base directory

./build.sh readme

```

This command can be run in container, by entering a shell in the inner environment

```{sh, eval = FALSE}

# externally, in project base directory

./runtime.sh sh

# internally, in project base directory

./build.sh readme

```



  
## Document Sample

### Code Evaluation

```{r, eval = TRUE}

salutation <- c( 
  dummy_hello(),
  dummy_hello("Earth"),
  dummy_hello("Moon", "'Night")
)

cat(salutation)

```



## Script Execution

### in Rsession

```{r, eval = TRUE}

# in project base directory

source("exec/dummy_runner.R")

```

### from command-line (inside container)

```{sh, eval = FALSE}

# in project base directory

./starter.sh


```

### from command-line (outside container)

```{sh, eval = FALSE}

# in project base directory

./worker.sh pack,exec


```


## Sample Usage

## GitLab Installation


```{r, eval = FALSE}

# install from gitlab
# install.packages("devtools")
devtools::install_gitlab("ub-dems-public/ds-labs/dve-sample-r")

```

### Basic demo
  
* `dummy_hello()` get default salutation


